\section{Prototyp structure}
\label{ch:practical_realization:prot_struct}
The following project structure in listing \ref{ch:practical_realization:struc} gives an overview of the prototyp and of how it is built in this paper.
\lstinputlisting[caption={Prototyp structure in Python}, captionpos=b, label={ch:practical_realization:struc}]{chapters/main/practical/listings/struc.txt}

The root folder contains the main program the analysing\_manager.py, a modules folder and the venv directory.
The venv directory builds the virtual environment feature of Python, while the modules folder contains the essential modules which represents the core function of the prototyp, namely obtaining-, preprocessing-, mounting- and scanning module. These python-modules represents the modules in section \ref{ch:theory:analysing_process} from the theoretical concept. These are managed and used by an analysing\_manager module which lies in parent (root) folder. 

The analysing\_manager module is mainly in interaction with the core modules. The core modules are deliberately created as distinct units. That makes it easier to maintain the prototyp. Changing a single core module promises more flexibility and counteracts problems instead of maintaining a large monolith. A replacement of core modules is also possible since the interface to the analysing\_manager is untouched.
Through the analysing manager module a central endpoint exists to request the prototyp. This is especially useful for a potential microservice. Restpoints have a single place to interact with and to start the analysing. Also other common technologies like RPC's from Apache thrift or Googles protocol buffer can be used to trigger this single analysing endpoint. 

When the analysing manager is triggered with an image name as input, the procedure which is shown belowwill automatically starts.
\lstset{language=Python}          % Set your language (you can change the language for each code-block optionally)
\begin{lstlisting}[]  % Start your code-block
	
    analysing = AnalManager(img_name)
    analysing.prepare_environment()
    analysing.preprocess()
    if analysing.necessary:
         analysing.mount()
         analysing.examine()
    
\end{lstlisting}
It starts first with analysing.prepare\_environment() where the obtaining module \ref{ch:practical_realization:implementation:obtain} is executing its tasks. The Docker image will be downloaded by this module. Afterwards the preprocessing will take place through the call of the preprocess method. The preprocessing will be done by the implemented preprocessing module \ref{ch:practical_realization:implementation:preprocessing}.
Finally the analysing manager can decide if a further investigation is necessary. If so the mount and scan module will be instantiated. The synchronous mount call, as well as the examine call is is executed consecutively. The final result of the scan module is just printed out into the stdout stream of Linux.
\graffito{Note: Stdout, also known as standard output, is the default file descriptor where a process can write output.}
When secrets are found, the secret will be printed to the stdout stream. When no secret was found, a standard info message will be piped into the stdout buffer.

This section has given an overview about the implementation of the prototyp in general. The following section will introduce the implementation of the core modules.

